Constraint Programming - Inside Gecode

### 2014-05-08 paper.tex
corrections

	\begin{abstract}	
		Constraint programming is a way to describe and solve mathematical problems with arbitrary constraints. In the following paper I will explain the implemented algorithms in Gecode, a tool which can be used to solve problems through constraint programming.
	\end{abstract}

@@

	A solver for constraint programming like \emph{Gecode} provides the necessary tools to define constraints like \refeq{eq:squares} in their most natural form as equations and inequations and will find all possible solutions or just one of them, depending on the selected algorithm. If there would be only linear constraints like it would be possible to solve this problem through linear programming \cite[1]{linearProgramming}. As linear programming is only a subset of constraint programming the latter one is the more general one with more practical applications; not every problem in the real world is linear or can be linearized in a useful way. Consequently, constraint programming with its ability to consider constraints in their most general form can be used in various fields like scheduling of resources, computer-aided design and robotics \cite[p.~221]{trendsInCP}.

@@

	Constraints in \emph{Gecode} are always evaluated ahead of a further growth of a subtree, as it may be possible to prune some of the subtrees. The problem here is to decide in which order the constraints should be considered, and it may even be necessary to evaluate some constraints more often. A short example will explain this very well \cite[p.~575]{handbookCP}: Let there be two constraints 
	\begin{equation}
		c_1: y - x^2 = 0
	\end{equation}
	\begin{equation}
		c_2: y - x - 1 = 0
	\end{equation}
	and let the variable domains be $x, y \in [-4, 4]$. Starting with the evaluation of constraint one follows a chain of reductions of the variable domains, based only on constraint propagation:
	\begin{equation}
	\begin{split}
		c_1:\ &y \in [-4, 4] \rightarrow y \in [0, 4] \\
		c_1:\ &x \in [-4, 4] \rightarrow x \in [-2, 2] \\
		c_2:\ &y \in [0, 4] \rightarrow y \in [0, 3] \\
		c_2:\ &x \in [-2, 2] \rightarrow x \in [-1, 2] \\
		c_1:\ &x \in [-1, 2] \rightarrow x \in [-1, 1.73 \dots] \\
		&\dots
	\end{split}
	\end{equation}

>>>>

	\begin{abstract}	
		Constraint programming is a way to describe and solve mathematical problems with arbitrary constraints. In the following paper I will explain the implemented algorithms in \emph{Gecode}, a tool which can be used to solve problems through constraint programming.
	\end{abstract}

@@

	A solver for constraint programming like \emph{Gecode} provides the necessary tools to define constraints like \refeq{eq:squares} in their most natural form as equations and inequations and will find all possible solutions or just one of them, depending on the selected algorithm. If there would be only linear constraints like \refeq{eq:linear} it would be even possible to solve the problem through linear programming \cite[1]{linearProgramming}. As linear programming is only a subset of constraint programming the latter one is the more general one with more practical applications; not every problem in the real world is linear or can be linearized in a useful way. Consequently, constraint programming with its ability to consider constraints in their most general form can be used in various fields like scheduling of resources, computer-aided design or robotics \cite[p.~221]{trendsInCP}.

@@

	Constraints in \emph{Gecode} are always evaluated ahead of a further growth of a subtree, as it may be possible to prune some of the subtrees. The problem here is to decide in which order the constraints should be considered, and it may even be necessary to evaluate some constraints more often. A short example will explain this very well \cite[p.~575]{handbookCP}: Let there be two constraints 
	\begin{equation}
		c_1: y - x^2 = 0
	\end{equation}
	\begin{equation}
		c_2: y - x - 1 = 0
		\label{eq:linear}
	\end{equation}
	and let the variable domains be $x, y \in [-4, 4]$. Starting with the evaluation of constraint one follows a chain of reductions of the variable domains, based only on constraint propagation:
	\begin{equation}
	\begin{split}
		c_1:\ &y \in [-4, 4] \rightarrow y \in [0, 4] \\
		c_1:\ &x \in [-4, 4] \rightarrow x \in [-2, 2] \\
		c_2:\ &y \in [0, 4] \rightarrow y \in [0, 3] \\
		c_2:\ &x \in [-2, 2] \rightarrow x \in [-1, 2] \\
		c_1:\ &x \in [-1, 2] \rightarrow x \in [-1, 1.73 \dots] \\
		&\dots
	\end{split}
	\end{equation}
